DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-09-29 paper/main.tex
Add parts of platform overview and modify figures

\section{Platform Overview}
...
\section{Data Collection}
...
\section{Network Architecture}
...
\section{Real-Time DNN Inferencing}
...
\section{Online/Offline Training}
...
\section{Evaluation}
In evaluating the real-time efficacy of the Raspberry Pi 3, the same methodology is utilized in all 
experiments conducted. The performance of the Pi is measured over a set of 1001 video frames that are 
each individually fed to the model. The processing time for the first frame is ignored as, due to 
cache warmup, it is uncharacteristically high and doesn't accurately represent the Pi's capabilities. A 
deadline of 50 ms, or 20 Hz, is used as a baseline to assess the Pi's ability to complete all 
necessary real-time operations in a timely manner. Also, please note that frame processing times 
would be approximately the same if the input stream was a 
camera instead of a video.

\subsection{Real-Time Operations}
In our platform, three main real-time tasks are performed during autonomous operation. 
In order, those operations are: (1) capturing and reading the input frame from the designated camera 
or video stream, (2) preprocessing the acquired frame so that it is compatible with the DNN, and (3) 
feeding the frame to and getting the angle prediction from the model. However, the time it takes to 
complete each of the operations will differ, with at least one of them being the dominating step in 
processing each frame.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{Operation_Time}
  \caption{ Real-time operation completion time in processing frames.}
\end{figure}

@@

\begin{table*}
  \begin{tabular} {| l | l | l | l | l | l | l | l | l | l |}
    \hline
    \textbf{num cores} & \textbf{mean} & \textbf{max} & \textbf{99.999pct} & \textbf{99.99pct} & 
      \textbf{99.9pct} & \textbf{99pct} & \textbf{min} & \textbf{median} & \textbf{stdev} \\ \hline 
    1 & 61.95813584 & 65.99712 & 65.99277693 & 65.9536558 & 65.562445 & 63.30799 & 59.304 & 61.975479 & 
      0.506466 \\ \hline
    2 & 50.49184 895 & 71.54608 & 71.5404019 & 71.4893194 & 70.978494 & 70.02651 & 46.93723 & 50.011516 & 
      3.162015 \\ \hline
    3 & 48.11392045 & 72.21985 & 72.21789317 & 72.200294 & 72.024303 & 58.44643 & 41.15391 & 48.444033 & 
      4.178325 \\ \hline
    4 & 42.66992688 & 56.36907 & 56.33994633 & 56.0778672 & 53.457076 & 50.70305 & 38.26094 & 42.286992 & 
      2.800991 \\
    \hline
  \end{tabular}
  \caption{Real-time performance of the Raspberry Pi 3 depending on the number of cores used.}
\end{table*}

@@

\begin{table*}[t]
  \begin{tabular} {| l | l | l | l | l | l | l | l | l | l |}
  \hline
  \textbf{num models} & \textbf{cores} & \textbf{mean} & \textbf{max} & \textbf{L1 refs} & \textbf{L1 
    misses} & \textbf{L1 miss \%} & textbf{L2 refs} & \textbf{L2 misses} & \textbf{L2 miss \%} \\ \hline
  1 & 0 &  62.48010421 & 66.83707237 & 27,809,824,750 & 435,932,903	& 1.568 & 2,830,285,204	& 
    358,764,318 & 12.68 \\ \hline
  1 & 0,1 & 51.35843444 & 72.92294502 & 30,354,597,625 &  477,953,407 & 1.575 & 3,308,819,327 & 
    367,823,926 & 11.12 \\ \hline
  2 & 0,1 & 58.03400564 & 83.67586136 & 30,426,714,898 & 490,709,126 & 1.613 & 3,912,431,599 & 
    425,658,305 & 10.88 \\ \hline
  2 & 2,3 & 56.39569068 & 82.88908005 & 30,350,459,058 & 480,166,192 & 1.582 & 3,877,553,207 & 
    421,339,847 & 10.87 \\ \hline
  4 & 0 & 77.90289187 & 104.2420864 & 27,853,570,186 & 452,700,705 & 1.625 & 3,360,219,598 & 
    443,088,325 & 13.19 \\ \hline
  4 & 1 & 78.88618684 & 108.7918282 & 27,868,355,666 & 464,332,042 & 1.666 & 3,415,627,978 & 
    437,962,230 & 12.82 \\ \hline
  4 & 2 & 77.80583382 & 111.9449139 & 27,799,436,982 & 444,828,792 & 1.6 & 3,449,341,398 & 440,580,899 
    & 12.77 \\ \hline
  4 & 3 & 77.86954451 & 99.28488731 & 27,875,785,919 & 445,229,272 & 1.597 & 3,408,895,945 & 
    439,091,391 & 12.88 \\
  \hline
  \end{tabular}
  \caption{Real-time performance of the Raspberry Pi 3 depending on the number of models being run 
    simultaneously.}
\end{table*}

@@

>>>>

\section{Platform Overview}

\begin{figure}[h]
  \centering
  \includegraphics[width=.4\textwidth]{Picar_Picture}
  \caption{ The Picar Platform. }
\end{figure}

\subsection{Platform Components}
We employ a small and relatively inexpensive RC car that is capable of performing basic automotive 
operations. However, the car we use doesn't replicate the capabilities of other autonomous vehicle 
platforms, as it is more simplistic in nature. Notably, the RC car we use only has three possible 
options in terms of turning: center, left, and right. As such, control of the car may be less precise at 
times, and may negatively affect performance. The car is capable of other operations that aren't used 
within the scope of this platform. Specifically, the car is able to drive in reverse and the driving 
speed can be changed. In our experiments, we have the RC car drive forward, and at a constant speed.

Our platform also comes equipped with a camera that is used for both recording training videos and 
providing input frames to the model whenever the Picar is self-driving. We chose the Playstation Eye 
Camera due to its ability to reach and maintain higher fps levels while also remaining relatively 
low-cost. One concern, however, is the affect of camera latency on the self-driving performance of our 
platform. While humans are able to see environmental changes in real-time, the same can't be said for 
cameras since there is a delay between when frame capture by the camera, and when it is read by the 
Raspberry Pi 3. As a result, it is possible for the model to be given an input frame that is different 
from the real world, thus impacting the performance of the Picar.

\subsection{Model Training}
In order to operate the Picar as an autonomous vehicle, we utilize the DeepTesla library, which is 
capable of training a deep neural network (DNN) with end-to-end learning, that could then be used by the 
Picar for autonomous driving. Please note that it is more efficient to execute the actual model training 
process on a different system with an NVIDIA GPU, rather than on the Raspberry Pi 3 itself. This is 
because DeepTesla trains the DNN with the Tensorflow library, which greatly benefits from the use of 
gpu-enabled operations. For comparison, training a model on the Pi took approximately 6 hours, whereas 
the time it took on a computer with a NVIDIA GPU was only around 5 minutes!

We train our model on a custom made track/lane composed of black and white duct tape, where the black 
tape represents the bounds of the track, and the white tape marks the center of the lane. The model is 
taught to stay close to the center of the lane for as long as possible, and to turn whenever it 
reaches/crosses the outer lane bounds so that it remains on the track. For data, we navigate and record 
the car going both ways across the track, and use the collected videos to train the model(s) that will 
be used later for angle prediction while the car is self-driving.

\section{Data Collection}
...
\section{Network Architecture}
...
\section{Real-Time DNN Inferencing}
...
\section{Online/Offline Training}
...
\section{Evaluation}
In evaluating the real-time efficacy of the Raspberry Pi 3, the same methodology is utilized in all 
experiments conducted. The performance of the Pi is measured over a set of 1001 video frames that are 
each individually fed to the model. The processing time for the first frame is ignored as, due to 
cache warmup, it is uncharacteristically high and doesn't accurately represent the Pi's capabilities. A 
deadline of 50 ms, or 20 Hz, is used as a baseline to assess the Pi's ability to complete all 
necessary real-time operations in a timely manner. Also, please note that frame processing times 
would be approximately the same if the input stream was a 
camera instead of a video.

\subsection{Real-Time Operations}
In a real-time operations, the system has to be capable of consistently executing all necessary 
functions before their given deadlines. In the case of our platform, it has to process every given frame 
and get the predicted angles from the model. In order to determine if the Raspberry Pi 3 is capable of 
this, we tested the platform and recorded the time it took for the Pi to complete all real-time 
functions for every given frame.For this experiment, all four of the Pi's cpu cores were utilized, and 
only one model was run. As can be seen in Figure 1, the Pi was able to meet almost all of its deadlines, 
while only missing it in a few instances.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{Total_Processing_Time}
  \caption{ Real-time performance of the Raspberry Pi 3 in processing 1000 frames.}
\end{figure}

In our platform, three main real-time tasks are performed during autonomous operation. 
In order, those operations are: (1) capturing and reading the input frame from the designated camera 
or video stream, (2) preprocessing the acquired frame so that it is compatible with the DNN, and (3) 
feeding the frame to, and getting the angle prediction from, the model. However, the time it takes to 
complete each of the operations will differ, with at least one of them being the dominating step in 
processing each frame.

\begin{table}[h]
  \centering
  \begin{tabular} {| l | l | l | l | l |}
    \hline
    \textbf{operation} & \textbf{mean} & \textbf{max} & \textbf{99pct} & \textbf{stdev} \\ \hline 
    Frame Capture & 2.28 & 4.94 & 63.31 &  .51\\ \hline
    Preprocessing & 3.09 & 4.6 & 3.31 & .1 \\ \hline
    Angle Prediction & 37.3 & 51.03 & 45.48 & 2.75 \\ 
    \hline
  \end{tabular}
  \caption{Real-time performance of the Raspberry Pi 3 depending on the number of cores used.}
\end{table}

@@

\begin{table}[h]
  \centering
  \begin{tabular} {| l | l | l | l | l | l | l | l | l | l |}
    \hline
    \textbf{num cores} & \textbf{mean} & \textbf{max} & \textbf{99pct} & \textbf{stdev} \\ \hline 
    1 & 61.96 & 66 & 63.31 &  .51\\ \hline
    2 & 50.49 & 71.55 & 70.03 & 4.18 \\ \hline
    3 & 48.11 & 72.22 & 58.45 & 2.8 \\ \hline
    4 & 42.67 & 56.37 & 50.70 & 2.8 \\
    \hline
  \end{tabular}
  \caption{Real-time performance of the Raspberry Pi 3 depending on the number of cores used.}
\end{table}

@@

\begin{table*}
  \begin{tabular} {| l | l | l | l | l | l | l | l | l |}
  \hline
  \textbf{num models} & \textbf{cores} & \textbf{mean} & \textbf{L1 refs} & \textbf{L1 
    misses} & \textbf{L1 miss \%} & textbf{L2 refs} & \textbf{L2 misses} & \textbf{L2 miss \%} \\ \hline
  1 & 0,1 & 51.35 & 3.04E+10 & 4.78E+08 & 1.58 & 3.31E+09 & 3.68E+08 & 11.12\\ \hline
  2 & 0,1 & 58.03 & 3.04E+10 & 4.91E+08 & 1.61 & 3.91E+09 & 4.26E+08 & 10.88 \\ \hline
  2 & 2,3 & 56.4 & 3.04E+10 & 4.80E+08 & 1.58 & 3.88E+09 & 4.21E+08 & 10.87 \\ \hline
  \end{tabular}
  \caption{Real-time performance of the Raspberry Pi 3 when 2 models are running simultaneously.}
\end{table*}

@@

\begin{table*}
  \begin{tabular} {| l | l | l | l | l | l | l | l | l |}
  \hline
  \textbf{num models} & \textbf{core} & \textbf{mean} & \textbf{L1 refs} & \textbf{L1 
    misses} & \textbf{L1 miss \%} & textbf{L2 refs} & \textbf{L2 misses} & \textbf{L2 miss \%} \\ \hline
    1 & 0 &  62.48 & 2.78E+10 & 4.36E+08 & 1.57 & 2.83E+09 & 3.59E+08 & 12.68  \\ \hline
    4 & 0 & 77.9 & 2.79E+10 & 4.53E+08 & 1.63 & 3.36E+09 & 4.43E+08 & 13.19 \\ \hline
    4 & 1 & 78.89 & 2.79E+10 & 4.64E+08 & 1.67 & 3.42E+09 & 4.38E+08 & 12.82 \\ \hline
    4 & 2 & 77.81 & 2.78E+10 & 4.45E+08 & 1.6 & 3.45E+09 & 4.41E+08 & 12.77 \\ \hline
    4 & 3 & 77.87 & 2.79E+10 & 4.45E+08 & 1.60 & 3.41E+09 & 4.39E+08 & 12.88 \\ \hline
  \end{tabular}
  \caption{Real-time performance of the Raspberry Pi when 4 models are running simultaneously.}
\end{table*}
